---
title: "Supplementary material C - data package and model code"
author: RM Link, S Fuchs, D Arias Aguilar, C Leuschner M Castillo Ugalde, JC Valverde Otarola,  B Schuldt
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description
The present R project is part of the digital supplementary material of Link et al. (2019) -- *Tree height predicts the shape of radial sap flow profiles of Costa-Rican tropical dry forest tree species* -- and contains the Stan code for the three different hierarchical models considered in the paper (cf. Supplementary Material A for details about the model structure).

## Structure
The Stan model code is stored in the `/stan` folder, while the code for the simple frequentist models used to generate starting values is stored in `1_HFD_analysis_nlme.R` and the code used to fit the models is found in `1_HFD_analysis_stan.R`. 

The full project structure is as follows:
```{r, tidy=FALSE, eval=FALSE, highlight=FALSE }
/               top-level scripts:
                1_HFD_analysis_nlme.R   -- preliminary nlme-based models for starting values
                2_HFD_analysis_stan.R   -- final model fitting with Stan
/data           dataset used for model fitting
/output	        saved model objects, model output etc.
/R              scripts that are sourced by the top level scripts
                /R/get_starting_values_ABC.R   -- functions for randomized starting values based
                                                  on the maximum likelihood estimates
                /R/utility_functions.R         -- utility functions used in the top level scripts                                  
/stan           model code for the Stan models
                /stan/model_A*       -- simple model without species level random effects and 
                                        parameter regressions
                /stan_model_B*       -- model with full random effects but without parm. regressions
                /stan_model_C*       -- full model
                                                  
```
